A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-14 README.Rmd
clarifications and typos in README

This is the accompanying GitHub repository to a work in progress paper by Aaron Peikert[![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7813-818X) and Andreas Brandmaier [![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0001-8765-6982).

@@

## Usual Way

@@

## Using Workflow

>>>>

This is the accompanying GitHub repository to a work in progress paper by Aaron Peikert[![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7813-818X) and Andreas M. Brandmaier [![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0001-8765-6982).

@@

The following paragraphs describe how you can obtain a copy of the source files of our manuscript describing reproducible workflows, and create the PDF. Either, you can go the 'standard' way of downloading a local copy of the repository and knit the manuscript file in R, or you can use the reproducible workflow as suggested and use Make to create a container and build the final PDF file in exactly the same virtual computational environment that we used to render the PDF.

## Standard Way

@@

## Using a Reproducible Workflow
